### 2019-02-10 paper.tex
Final version

\item Users \emph{publish experiment results} to remote locations over
  SSH or cloud services like S3 where they are securely studied and
  compared by others.
\end{itemize}

@@

Each requirement that a tool imposes on a user presents a barrier to
the goal of systematic machine learning. In some cases, researchers
and engineers may view the cost of supporting reproducibility to
outweigh the benefits.

@@

With this command, the user generates a unique experiment with the
specified hyperparameters, which can be analyzed and compared to other
trials.

@@

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item \emph{Influence}. Work that is easier to reproduce is more
  likely to influence others, other factors being equal.

@@

\textbf{Scenarios}. The demonstration is structured flexibly to
encourage questions, input, and redirection from the audience. While
presented below as a sequence, scenarios are presented and discussed
in any order according to audience interest.

@@

\item \emph{Clegane} conducts a survey of related work, reproducing
  published results where possible. He clones Arya's repository and
  uses Guild to reproduce her findings. He further experiments with
  changes to Arya's model and hyperparameters to develop a deeper
  understanding for his summary.

@@

\item \emph{Arya} pulls Clegane's results from S3 and uses Guild to
  study the differences between her results and his. She uses this
  information to answer Clegane's questions.

>>>>

\item Users \emph{publish experiment results} to secure, remote
  locations over SSH or cloud services like S3 where they are studied
  and compared by others.
\end{itemize}

@@

Each requirement that a tool imposes on a user presents a barrier to
the goal of systematic machine learning. In some cases, users may view
the cost of supporting reproducibility to outweigh the benefits.

@@

With this command, the user generates a unique experiment with the
specified hyperparameters, which can be analyzed, compared to other
trials, and shared.

@@

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item \emph{Influence}. Work that is easier to reproduce is more
  likely to influence others.

@@

\textbf{Scenarios}. The demonstration is structured flexibly to
encourage questions, input, and redirection from the audience. While
listed below sequentially, scenarios are presented and discussed in
any order according to audience interest.

@@

\item \emph{Clegane} conducts a survey of related work, reproducing
  published results where possible. He clones Arya's repository and
  uses Guild to reproduce her findings. He further experiments with
  changes to Arya's model and hyperparameters to deepen his
  understanding for his report.

@@

\item \emph{Arya} pulls Clegane's results from S3 and uses Guild to
  study the differences between their results and uses this
  information to answer his questions.
